A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2015-09-30 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Add keywords and explanation about co-authorship

\author{Annika Siders\inst{1} \and Bruno Woltzenlogel Paleo\inst{2}}

@@

\institute{
  Helsinki, Finland\\
  \email{annika.siders@helsinki.fi}
  \and 
  Vienna, Austria ; Canberra, Australia \\
  \email{bruno.wp@gmail.com}
}

@@

>>>>

\author{Annika Siders\inst{1} \and Bruno Woltzenlogel Paleo\inst{2}\thanks{Both co-authors contributed equally to this paper. Author order is alphabetical by surname. Bruno Woltzenlogel Paleo is the corresponding author.}}

@@

\institute{
  Helsinki, Finland\\
  \email{annika.siders@helsinki.fi}
  \and 
  Vienna University of Technology, Austria ; Australian National University \\
  \email{bruno.wp@gmail.com} 
}

@@

\begin{abstract}
ToDo: 200 words
\end{abstract}

\noindent
\textbf{Keywords: } Higher-Order Modal Logics, Ontological Proof, Natural Deduction
